Structuring College Access

### 2025-02-19 index.qmd
la la

- Correlations from training data caused by structural inequality
  - "Predicting the future on the basis of the past threatens to reify and reproduce existing inequalities" [@RN4794, p. 224]
- @RN4982 find 4 predictors of student market segment
  - Parental education, family income, SAT score, educational aspirations
  - Recommend selective colleges target high-SES Geomarkets

>>>>

- Correlations observed in training data caused by structural inequality
  - "Predicting the future on the basis of the past threatens to reify and reproduce existing inequalities" [@RN4794, p. 224]
- @RN4982 find 4 predictors of student market segment
  - Parental education, family income, SAT score, educational aspirations
  - Recommend selective colleges target high-SES Geomarkets
